Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-05-31 paper.tex
Adding more detail to LWB evo

A time-dependent LW optically thin radiation background is applied in the simulation. This was fit in W12 (see their Eq. 16) and is consistent with the values in \citet{Trenti09_SFR}. The background evolution of the specific intensity takes the following form:
\begin{equation} \label{LWbg}
	\log_{10}(J_{\rm LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
\end{equation}
where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.  This form gives a maximum of $J_{\rm LW}/J_{21} = 0.85$ at a redshift of 13.5 and quickly and continually declines for higher redshifts. We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field. Centered on each metal-enriched and Pop III star particle, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile. These LW sources are added on top of the background intensity described above.
%====================================================================
\subsection{Star formation}
%====================================================================
In this section, we briefly discuss our implementation of Pop III and metal-enriched star formation. We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars. For further details, we refer the reader to W12.

>>>>

A time-dependent LW optically thin radiation background is applied in the simulation. This was fit in W12 (see their Eq. 16) and is consistent with the values in \citet{Trenti09_SFR}. The background evolution of the specific intensity takes the following form:
\begin{equation} \label{LWbg}
	\log_{10}(J_{\rm LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
\end{equation}
where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.  This form only varies by a factor of five in $z = 9-25$ and has a maximum of $J_{\rm LW}/J_{21} = 0.97$ at a redshift of 13.5 and slowly declines to 0.60 $J_{21}$ at $z = 9$ when we halt the simulation. We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field. Centered on each metal-enriched and Pop III star particle, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile. These LW sources are added on top of the background intensity described above.
%====================================================================
\subsection{Star formation}
%====================================================================
In this section, we briefly discuss our implementation of Pop III and metal-enriched star formation. We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars. For further details, we refer the reader to W12.
